Jeff Goldsmith

### 2017-04-08 teaching.Rmd
added link from teaching page to linear regression site

Spring 2016: Linear Regression Models  
Spring 2015: Linear Regression Models  
Summer 2015: Applied Regression II  
Spring 2014: Linear Regression Models  
Spring 2014: Categorical Data Analysis  
Spring 2013: Linear Regression Models  
Spring 2013: Categorical Data Analysis

@@

2017: ["Variable Selection Methods in Functional Regression"](https://jeff-goldsmith.github.io/IWAFDA/) (at the International Workshop on Advances in Functional Data Analysis)  
2014: "Functional Data Analysis: Techniques and Applications" (at ENAR)

>>>>

Spring 2016: [Linear Regression Models](http://jeffgoldsmith.com/P8111/)  
Spring 2015: Linear Regression Models  
Summer 2015: Applied Regression II  
Spring 2014: Linear Regression Models  
Spring 2014: Categorical Data Analysis  
Spring 2013: Linear Regression Models  
Spring 2013: Categorical Data Analysis

@@

2017: ["Variable Selection Methods in Functional Regression"](http://jeffgoldsmith.com/IWAFDA/) (at the International Workshop on Advances in Functional Data Analysis)  
2014: "Functional Data Analysis: Techniques and Applications" (at ENAR)
